---
title: "Advent of Code"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This repository is for sharing my code that I've made for Advent of Code using R. 

Each day I work on a puzzle, I'll add my code to a file and include my comments. In general, I'm striving to do things in the form of functions and avoiding defaulting to my natural space of using the tidyverse pipelines (Not that it's bad/wrong to use those, I just want to practice using closer to base functions)

```{r make table, echo=FALSE,message=FALSE,warning=FALSE}
library(tidyverse)

tribble(
  ~ date      , ~`puzzle name`,       ~`number of parts`,             ~code, 
  "2020-12-01", "Find Sum Components", 2 , "[link](https://github.com/delabj/advent_of_code/blob/master/R/day_01.R)", 
  "2020-12-02", "Password Validation", 2 , "[link](https://github.com/delabj/advent_of_code/blob/master/R/day_2.R)", 
  "2020-12-03", "Sleds and Trees"    , 2 , "[link](https://github.com/delabj/advent_of_code/blob/master/R/day_03.R)", 
  "2020-12-04", "Sleds and Trees"    , 2 , "[link](https://github.com/delabj/advent_of_code/blob/master/R/day_04.R)",
  "2020-12-05", "Fly like paper ✈️"  , 2 , "[link](https://github.com/delabj/advent_of_code/blob/master/R/day_05.R)" 

  ) %>%
  knitr::kable()


```

If you want to talk about the code feel free to open an issue of tag me on [twitter](http://www.twitter.com/delabjl).


